Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel.tex
ll
notation change in llevel proof

 For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.  Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{t,a,t_1,t_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
\]

Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$). By union bound, we have
\[
\Pr[W_2] \geq 1- \frac{4}{T^3}.
\]

@@

\xhdr{Proof Sketch.}
We still wlog assume arm 1 has the highest mean (i.e. $\mu_1 \geq \mu_a, \forall a \in \A$. We first extend the clean events (i.e. $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2. $W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,t_1,t_2} W_2^{t,a,t_1,t_2}$. The difference is that now $a$ is taken over $K$ arms instead of 2 arms. For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$. We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$. Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$. So the case when some clean event does not happen contributes $O(1)$ to the regret.

>>>>

 For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.  Define $W_2^{t,a,\z_1,\z_2}$ to be the event that the mean of $\z_1$-th to $\z_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{\z_2-\z_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{t,a,\z_1,\z_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
\]

Define $W_2$ to be the intersection of all these events (i.e. $W_2 = \bigcap_{t,a,\z_1,\z_2} W_2^{t,a,\z_1,\z_2}$). By union bound, we have
\[
\Pr[W_2] \geq 1- \frac{4}{T^3}.
\]

@@

\xhdr{Proof Sketch.}
We still wlog assume arm 1 has the highest mean (i.e. $\mu_1 \geq \mu_a, \forall a \in \A$. We first extend the clean events (i.e. $W_1,W_2,W_3,W_4$) in Theorem \ref{thm:llevel} to the case when $K$ is larger than 2. $W_1$ and $W_2$ extend naturally: we still set $W_1 = \bigcap_{a,s}W_1^{a,s}$ and $W_2 = \bigcap_{t,a,\z_1,\z_2} W_2^{t,a,\z_1,\z_2}$. The difference is that now $a$ is taken over $K$ arms instead of 2 arms. For $W_3$, we change the definition $W_3^{l,a} = \bigcup_u \left(W_3^{l,u,a,high}  \cap \left(\bigcap_{a' \neq a} W_3^{l,u,a',low}\right) \right)$ and $W_3 = \bigcap_{l,a} W_3^{l,a}$. We extend $W_4$ in a similar way: define $W^{a}_4$ as $\bigcup_u \left(W_4^{u,a,high} \cap \left(\bigcap_{a' \neq a} W_4^{u,a',low}\right) \right)$ and $W_4 = \bigcap_a W^a_4$. Since $K$ is a constant, it's easy to check that the same proof technique shows that the intersection of these clean events happen with probability  $1-O(1/T)$. So the case when some clean event does not happen contributes $O(1)$ to the regret.
